Minimum Regret Search for Single- and Multi-Task Optimization

### 2016-05-19 2016_ICML/cmrs.tex
Discussing bias in approximation section

Firstly, we approximate $\mathbb{E}_{p(f)}$ by taking $n_f$ Monte Carlo samples
from $p(f)$, which is straightforward in the case of GPs.
Secondly, we approximate $\mathbb{E}_{y \vert p(f), \mathbf{x}^q}$  by taking
$n_y$ Monte Carlo samples from $p(f)$'s predictive distribution at
$\mathbf{x}_q$. And thirdly, we discretize $p^\star$ to a finite set of $n_r$
representer points chosen from a non-uniform measure, which turns
$\mathbb{E}_{\mathbf{\tilde x} \sim p^\star_n}$ in the definition of
$\text{MRS}(\mathbf{x}^q)$ into a weighted sum. The discretization of $p^\star$ is discussed by
\citet{hennig_entropy_2012} in detail; we select the representer points as
follows: for each representer point, we sample $250$ candidate points uniform
randomly from $\mathcal{X}$ and select the representer point by Thompson
sampling from $p(f)$ on the candidate points. Moreover, estimating $p^\star_n$ on the
representer points is relatively cheap as we can reuse the samples used for approximating $\mathbb{E}_{p(f)}$.

>>>>

Firstly, we approximate $\mathbb{E}_{p(f)}$ by taking $n_f$ Monte Carlo samples
from $p(f)$, which is straightforward in the case of GPs.
Secondly, we approximate $\mathbb{E}_{y \vert p(f), \mathbf{x}^q}$  by taking
$n_y$ Monte Carlo samples from $p(f)$'s predictive distribution at
$\mathbf{x}_q$. And thirdly, we discretize $p^\star$ to a finite set of $n_r$
representer points chosen from a non-uniform measure, which turns
$\mathbb{E}_{\mathbf{\tilde x} \sim p^\star_n}$ in the definition of
$\text{MRS}(\mathbf{x}^q)$ into a weighted sum. The discretization of $p^\star$ is discussed by
\citet{hennig_entropy_2012} in detail; we select the representer points as
follows: for each representer point, we sample $250$ candidate points uniform
randomly from $\mathcal{X}$ and select the representer point by Thompson
sampling from $p(f)$ on the candidate points. Moreover, estimating $p^\star_{\mathcal{D}_n}$ 
on the representer points can be done relatively cheap by reusing the samples used 
for approximating $\mathbb{E}_{p(f)}$, which incurs a small bias which had, however, a negligible 
effect in preliminary experiments.
